\subsection{The Allen Brain Atlas}
Founded in 2003 by Microsoft co-founder Paul Allen, the Allen Institute for Brain Science is a nonprofit research organization dedicated to the public pursuit of brain research. Among the many free datasets provided by the Institute are the Allen Developing Mouse Brain Atlas (located at \href{http://www.developingmouse.brain-map.org/}{www.developingmouse.brain-map.org/}) and the Allen Atlas of the Developing Human Brain (located at \href{http://www.brainspan.org/}{www.brainspan.org/}).

The Developing Mouse Brain Atlas features in situ hybridization (ISH) data for over 2,100 genes across multiple stages of embryonic and postnatal mouse brain development. The raw images of the ISH scans total 434,946 images. These images were assembled into 3-dimensional grids of expression values.  In addition, an application programming interface (API) in the form of a bioinformatics pipeline allows researchers to access all data produced by the Developing Mouse Brain studies. The Developing Mouse API further allows researchers to obtain quantized expression values per region, which are calculated based off of analysis of the ISH scan images. These expression values may be found for several different developmental timepoints, at several discrete brain regions, for each of the 2,100+ genes. \cite{Thompson_2014}

Similar to the Developing Mouse Brain Atlas, the Developing Human Brain Atlas also features a diverse array of ISH expression values for several thousand genes. These expression values are available for download as raw comma-separated-values (CSV) files from the Developing Human Brain Atlas Website, although an API is still available. In addition to ISH images, extremely detailed, cellular-level, magnetic resonance imaging (MRI) and microarray data are also included. \cite{24695229}